-----
Title: ANP 846 Manuscript
Purpose: This study examines the statistical significance between waist to height ratio(WHtR) and several measurements in participants (n=507) aged 18 to 67. The skeletal measurements used originate from the pelvic area with bi-iliac measurement taken from the pelvic breadth, and bi-trochanteric measuring the diameter around what is typically the widest part of the hips. 
Publication:
Authors: Kaitlyn Szarenski (KS)
Last Updated on: 2025-12-2 (KS)

##### Updates:
1. 2025-9-10 (KS) Created base code chunks C1-3 titled, C1 - add random, set seed. C2 - Install and book OTE and tidyverse. C3 - Load in data and ensure proper matching. C4 - View data. MISC - set up header and add chunk directory

2. 2025-9-11 (KS) c4 - named, used to collect info for abstract and overview of dataset for better understanding. Results were added to notes

3. 2025-9-15 (KS) c5 - named, created some preliminary graphs to better understand what is included in bicrom and bi-iliac measurements, C6 - named, created objects in dataframe that find WHtR and take that and determine risk factor. C7 - named, creating filtered datasets

4. 2025-9-18 (KS) C8 - named, conducted outlier detection. C9 - named, linear regression models. C2- added function for flagging outliers

5. 2025-9-25 (KS) C4-added str to look at structure of dataset, added is.data.frame, added missing data screening and visualization C10, named

6. 2025-10-9 (KS) C10 - named, added in table for import to word

7. 2025-10-12 (KS) C11-named, created cor/var table

8. 2025-10-22 (KS) C2-added in libraries that may or may not be used but are commonly used 

9. 2025-11-29 (KS) c12-table generation, named, created tab1 tab2 tab3

10. 2025-11-30 (KS) c13-graph creation,named,created billi1,1

11. 2025-12-1 (KS) updated cor-cov table,created new table for age/gender, moved an unused plot to the graveyard

12. 2025-12-2 (KS) c16 - Find those packages, made code that identifys each unique instance of a package use and places it in a table

##### Notes: 
Age range 18-67
1 - male, 0 - female
measurements done in cm and kg

##### Chunk directory: 
C1 - Chunk 1 - working directory
C2 - Chunk 2 - library
C3 - Chunk 3 - data and function load
C4 - Chunk 4 - quick peak
C5 - Chunk 5 - prelim graphs
C6 - Chunk 6 - WHtR
C7 - Chunk 7 - Filtering
C8 - Chunk 8 - Outlier detection
C9 - Chunk 9 - linear regression
C10 - Chunk 10 - lm
c11 - Chunk 11 - Corr/cov table
c12 - Chunk 12 - Table generation for paper
c13 - Chunk 12 - Graph Creation
c14- Chunk 14 - next steps
c15 - Chunk 15 - Graveyard
c16 - Chunk 16 - Find those packages

-----

```{r working directory}
# Start with a clean working directory by clearing lists
rm(list=ls())
# Remove random
set.seed(1234)
```

```{r library}
if(!require('ggplot2')) {
  install.packages('ggplot2')
  library('ggplot2')
}
#Install package
#install.packages("OTE")
# load packages
library(OTE) #Contains the dataset "Body" that will be evaluated
library(tidyr) #used in chunks:
library(psych) #used in chunks: c4
library(ggplot2) #used in chunks: c5
library(dplyr)
library(kableExtra) #c11
library(pheatmap) #c11
library(dendextend)#c11
library(mice)
library(naniar)
library(forcats)
library(GGally)
library(gt)
library(viridis)
library(RColorBrewer)
library(plotly)
library(reshape2)
library(gridExtra)
library(descr)
options(descr.plot=FALSE)
library(plyr)
library(ggthemes)
library(stringr)
library(FactoMineR)
library(MASS)
library(ggdendro)
library(ape)
library(corrplot)
library(gtsummary) #c12
library(ggsignif) #c13, may not use
library(ggpubr) #c13, to do sig
library(tibble)#for the corcov table
library(webshot2)#export those gt tables that are being stupid and don't want to be exported for some god forsaken reason
library(patchwork)#for da legends oooo



```

```{r data and function load}
# Load Data
data <- Body #Source: https://rdrr.io/cran/OTE/man/Body.html
# Rename Data
bdy <- data

#rename gender to match
bdy$Gender <- ifelse(bdy$Gender== 0,"Female","Male")
bdy$Gender

plt1.1 <- ggplot(bdy,aes(Age,fill=Gender))+geom_density(alpha=0.25,linewidth=0.5)+
  theme_classic()+
  scale_fill_manual(values=c("#fc8d62","#66c2a5"))+
  labs(y="Density")
#ggsave("agedist.png", plot = plt1.1, width = 8, height = 6, dpi = 300)

bdy$age_grouping <- cut(bdy$Age, seq(10, 70, 10),
                        labels = c("10-20", "21-30", "31-40", "41-50", "51-60","61-70"))
bdy$age1 <- bdy$Age

bdy$Age <- bdy$age_grouping

#bdy$Age <- bdy$age_grouping

###load functions###
flag_outliers <- function(x) {
  q <- quantile(x,probs = c(.25,.75), na.rm=TRUE)
  iqr <- q[2]-q[1]
  upper <- q[2]+1.5*iqr
  lower <- q[2]-1.5*iqr
  x<lower|x>upper
}

pvals <- function(i,j) mapply(function(a,b) cor.test(bdy[[a]], bdy[[b]])$p.value, i, j)

#pvals if sig get stars
stars <- function(p) {
  if (p < .05)  return("*")
  return("")
}



```

```{r quick peak}
#summary of data to double check that all objects match at this stage
#summary(Body)
#summary(data)
#summary(body)

#look at data briefly
bdy
str(bdy)
describe(bdy)
dim(bdy)
colSums(is.na(bdy))
summary(bdy)
#missing data screening
is.data.frame(bdy)
if(requireNamespace("naniar",quietly=TRUE)){naniar::vis_miss(bdy)}
count(bdy$Gender==1)



```

Finding the inital distrabution of variables of interest
```{r prelim graphs}

ggplot(bdy,aes(Biiliac))+geom_histogram(bins=40)+theme_classic()+labs(x="Billiac measurement in cm", y= "Number of people")
ggplot(bdy,aes(Biacrom))+geom_histogram(bins=30)+theme_classic()+labs(x="Bicrom measurement in cm", y= "Number of people")


```

Creation of Waist to Height Ratio is established by dividing waist circumference in cm by height in cm. A WHtR greater than 0.5 for people under the age of 50 is established as higher risk and 0.6 for those over 50
```{r WHtR}
bdy$whtr <- bdy$WaistG/bdy$Height


bdy$whtrrisk <- ifelse(bdy$whtr>0.6 & bdy$age1 >50, "High Risk",
                   ifelse(bdy$whtr>0.5 & bdy$age1<51, "High Risk","Low Risk"))
```

BMI is established as weight in kg/height in m^2 a bmi over 30 is considered high risk for some health concerns
```{r BMI}
bdy$heightinm <- bdy$Height/100
bdy$bmi <- bdy$Weight/bdy$heightinm^2
bdy$bmirisk <- ifelse(bdy$bmi>=30, "High Risk", "Low Risk")

```

Create columns that include the labels for those at high risk, low risk for both wthr and bmi 
```{r filtering}
#risk of both whtr and bmi
athighrisk <- bdy%>%
  filter(whtrrisk =="High Risk", bmirisk == "High Risk")



#bmi risk and not at risk based on whtr
atbmirisk <- bdy%>%
  filter(bmirisk=="High Risk",whtrrisk!= "High Risk")

#at whtr risk but not bmi risk
atwhtrrisk <- bdy%>%
  filter(whtrrisk=="High Risk", bmirisk!= "High Risk" )

athighrisk
atbmirisk
atwhtrrisk
```

Recognize that there are no specimens that are at high risk based on bmi and are not at high risk based on the waist to height ratio therefore filtered data frame atbmirisk is empty. This is not true of at whtrrisk where there are 57 specimens that have been declared at high risk based ob the WHtR ration but are not at risk according to the bmi scale. There are 18 specimens that are declared at high risk from both the bmi scale as well as the WHtR risk assessment.

```{r outlier detection}


##biiliac

bdy$biiloutlier_by_strata <- ave(bdy$Biiliac,interaction(bdy$whtr,bdy$bmi), FUN= flag_outliers)
table(bdy$biiloutlier_global)
table(bdy$biiloutlier_by_strata)

bdy[bdy$biiloutlier_by_strata,]

whtrmean <- ggplot(bdy, aes(Biiliac,whtr,group=whtrrisk))+
  stat_summary(fun=mean,geom="point")+
  stat_summary(fun=mean,geom="line")+
  stat_summary(fun.data=mean_cl_normal, geom="errorbar", width=0.15)+
  facet_wrap(~whtrrisk)+
  labs( x= "Pelvic Breadth (cm)", y= "Waist to height ratio")+
  theme_classic()
bmimean <- ggplot(bdy, aes(Biiliac,bmi,group=bmirisk))+
  stat_summary(fun=mean,geom="point")+
  stat_summary(fun=mean,geom="line")+
  stat_summary(fun.data=mean_cl_normal, geom="errorbar", width=0.15)+
  facet_wrap(~whtrrisk)+
  labs(x= "Pelvic Breadth (cm)", y= "Body Mass Index")+
  theme_classic()

plotadd <- whtrmean+bmimean+ plot_layout(nrow = 2)

plotadd
#ggsave("ci.png",plotadd)
```

Linear regression modeling
```{r lm}
#biacrom
fit_aovbiacrom <- aov(Biacrom~whtr*bmi, data=bdy)
summary(fit_aovbiacrom)

fit_lmbiacrom <- lm(Biacrom~whtr*bmi, data=bdy)
summary(fit_lmbiacrom)
par(mfrow=c(2,2))
plot(fit_aovbiacrom)
par(mfrow=c(1,1))

#biiliac
fit_aovbiil <- aov(Biiliac~whtr*bmi, data=bdy)
summary(fit_aovbiacrom)

fit_lmbiil <- lm(Biiliac~whtr*bmi, data=bdy)
summary(fit_lmbiil)
par(mfrow=c(2,2))
plot(fit_aovbiil)
par(mfrow=c(1,1))
```


```{r cor/cov table}
bdy
which.variables <- c(2,27,31,28)
Breaks <- seq(-1, 1, by=.01)
# select a color palette
my_palette <- c( colorRampPalette( rev(RColorBrewer::brewer.pal(n = 11,
                                                                name ="Spectral")))(length(Breaks)-2) , "grey80", "grey80")

#find pvals
test <- bdy%>%
  dplyr::select(which.variables)
test


mt <- test

mt <- mt%>%
    dplyr::rename(
    `Waist to Height Ratio` = whtr,
    `Body Mass Index` = bmi,
    `Pelvic Bredth`=Biiliac,
    `Age`=age1
  )
mt
#write table
#my.mat <- outer(seq_len(ncol(mt)), seq_len(ncol(mt)), pvals)
#write.csv(my.mat,"pvals.csv")
#my.mat <- cor(bdy[,which.variables],use="p",method="p")
#pvals <- read.csv("pvals.csv")
#pvals

#diag(my.mat) <- apply(bdy[,which.variables],2,sd,na.rm=TRUE)
#my.mat[lower.tri(my.mat)] <- cov(bdy[,which.variables],use="p")[lower.tri(cov(bdy[,which.variables],use="p"))]

#####correlation, covariance, SD####
cor_mat <- cor(mt, use = "pairwise.complete.obs")
cov_mat <- cov(mt, use = "pairwise.complete.obs")
sd_vec  <- apply(mt, 2, sd, na.rm = TRUE)

# p-values for correlations only
get_pval <- function(x, y) cor.test(x, y)$p.value
pval_mat <- outer(
  seq_len(ncol(mt)),
  seq_len(ncol(mt)),
  Vectorize(function(i, j) get_pval(mt[, i],
                                    mt[, j]))
)

# Build combined numerical matrix
combined <- cor_mat
diag(combined) <- sd_vec
combined[lower.tri(combined)] <- cov_mat[lower.tri(cov_mat)]

# Prepare a character version so we can attach stars
combined_char <- matrix(
  as.character(round(combined, 3)),
  nrow = nrow(combined),
  ncol = ncol(combined),
  dimnames = dimnames(combined)
)

# Apply stars ONLY to upper triangle correlations,this piece of shit really wants to go into all of the sections
for (i in 1:ncol(cor_mat)) {
  for (j in 1:ncol(cor_mat)) {

    # Only upper triangle (correlations), like I said ONLY cor
    if (i < j) {
      p <- pval_mat[i, j]
      combined_char[i, j] <- paste0(combined_char[i, j], stars(p))
    }

    # diagonal and lower triangle remain unchanged (Thank god)
  }
}

# Convert to data frame so it can be tableized
trial1.7 <- as.data.frame(combined_char) %>%
  tibble::rownames_to_column("Variable")

trial1.7 <- gt(trial1.7, rowname_col = "Variable") %>%
  # Center column headers
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_column_labels(columns = everything())
  ) %>%
  # Center all body values
  tab_style(
    style = cell_text(align = "center"),
    locations = cells_body(columns = everything())
  ) %>%
  # Left-align row labels, i swear this better work I am so sick of the rows being center aligned, yipee it works, now why is there a line there
  tab_style(
    style = cell_text(align = "left"),
    locations = cells_stub()
  )%>%
  #Burn the witch (aka the line)
  tab_options(
    stub.border.width = px(0)
  )

#gtsave(trial1.7,"corcovsd.png")
##########################
#write.csv(my.mat,"cor_sd_covary.csv")

heatmapplot <- pheatmap(cor(bdy[,which.variables], use="p", method="p"), cluster_cols=TRUE,
         cluster_rows=TRUE, display_numbers = TRUE,
          breaks=Breaks,
         #labels_row = paste("Wave", 1:7),  labels_col = paste("Wave", 1:7),
         color= my_palette)

#ggsave("heatmapplot.png", plot = heatmapplot, width = 8, height = 6, dpi = 300)

which.vars2 <- c(1:21,23,24,27,28,30,31)
#heat map of all variables
heatmapplot2 <- pheatmap(cor(bdy[which.vars2], use="p", method="p"), cluster_cols=TRUE,
         cluster_rows=TRUE, display_numbers = TRUE,
          breaks=Breaks,
         #labels_row = paste("Wave", 1:7),  labels_col = paste("Wave", 1:7),
         color= my_palette)

#ggsave("heatmapplot2.png", plot = heatmapplot2, width = 8, height = 6, dpi = 300)

#plot cluster
plot(hclust(as.dist(1-cor(bdy[,which.variables],method="p"))), xlab="Distance: 1-correlation")

my.mat <- cor(bdy[,which.variables],use="p",method="s")
#my.mat <- ifelse(my.mat < 0.05, paste0("**", sprintf("%.2f", my.mat), "**"),sprintf("%.2f", my.mat))

diag(my.mat) <- apply(bdy[,which.variables],2,sd,na.rm=TRUE)
my.mat[lower.tri(my.mat)] <- cov(bdy[,which.variables],use="p")[lower.tri(cov(bdy[,which.variables],use="p"))]
write.csv(my.mat,"cor_sd_covary.csv")


#my.mat <- read.csv("cor_sd_covary.csv")
kable(my.mat, escape = FALSE) %>%
  kable_styling(full_width = FALSE)
kable(my.mat,digits=22,caption="Correlation/SD/coariances between variables") %>% kable_styling()



#distances of individuals based on complete observations and how they relate to each other
pheatmap(bdy[,which.variables],scale="row",color=my_palette,show_rownames = TRUE)
clust.compl <- hclust(dist(bdy[,which.variables]),method="complete")
plot(clust.compl)

table(cutree(clust.compl,k=5))
nodePar <- list(lab.cex=0.6,pch=c(NA,5), cex=0.7,col=my_palette)


dend <- as.dendrogram(hclust(dist(bdy[,which.variables]),method = "complete"),
                       nodePar=nodePar,leaflab="none")
dend1 <- color_branches(dend,k=5)
plot(dend1,type="rectangle",nodePar=nodePar,leaflab="none", ylab="Height",xlab="Individuals")
par(mfrow=c(1,1))
par(mar=c(12,4,1,1))
```

```{r table generation for paper}
#creating a missing variable table, no missing variables discard tableage1

min(bdy$age1)
max(bdy$age1)



tab1 <- bdy  %>%
  dplyr::select(Biacrom,Biiliac,Bitro,ChestDp,ChestD,ElbowD,WristD,KneeD,AnkleD,ShoulderG,ChestG,WaistG,AbdG,HipG,ThighG,BicepG,ForearmG,KneeG,CalfG,AnkleG,Age,Weight,Height,Gender
  ) %>%    miss_var_summary() %>%
  gt::gt() %>%
  gt::cols_label(
    variable = "Variable",
    n_miss = "Missing (count)",
    pct_miss = "Missing (%)"
  ) %>%
  gt::fmt_number(
    columns = c(pct_miss),
    decimals = 2
  )
tab1
###



tab2 <- bdy%>%
  dplyr::select(Age,Gender)%>%
  tbl_summary()

tab2
gt2 <- as_gt(tab2)
#gtsave(gt2,"age_group_by_gender.png")

###
tab2.1 <- bdy%>%
  dplyr::select(Age,Gender)%>%
  tbl_cross()

tab2.1
gt2.1 <- as_gt(tab2.1)
#gtsave(gt2.1,"age_group_and_gender.png")


  
  
####  
tab3 <- bdy%>%
  dplyr::select(age_grouping,whtrrisk,Gender)%>%
  mutate(Age = paste(age_grouping))%>%
   mutate(whtrrisk = paste(whtrrisk)) %>%
  tbl_strata(strata=Gender,
             .tbl_fun = ~.x %>%
               tbl_summary(by=whtrrisk,include = age_grouping,label = list(age_grouping ~ "Age Group"))%>%
               add_n(),
             .header = "**{strata}**",N={n}
            )
tab3
gt31 <- as_gt(tab3)
#gtsave(gt31,"WTHRRISK.png")

###
tab4 <- bdy%>%
  dplyr::select(Age,bmirisk,Gender)%>%
  
   mutate(bmirisk = paste(bmirisk)) %>%
  tbl_strata(strata=Gender,
             .tbl_fun = ~.x %>%
               tbl_summary(by=bmirisk)%>%
               add_n(),
             .header = "**{strata}**",N={n}
            )
tab4
gt4 <- as_gt(tab4)
gt4
#gtsave(gt4,"BMIRISK.png")


```

```{r graph creation}

billi1 <- ggplot(bdy,aes(whtrrisk,Biiliac,fill=Gender))+
  geom_boxplot()+
  geom_signif(comparisons = list(c("Low Risk","High Risk")),annotation = "*")+
  theme_classic()+
  scale_fill_manual(values=c("#fc8d62","#66c2a5"))

billi1.1 <- billi1+
  labs(x="Risk Establshed by Weight to Height Ratio",
       y= "Pelvic Bredth (cm)",
       fill="Gender")+
  theme(legend.position="bottom")

billi1.1
#ggsave("billi1.1.png", plot = billi1.1, width = 8, height = 6, dpi = 300)

#####ttesting#####
billit <- ggplot(bdy,aes(whtrrisk,Biiliac,fill=Gender))+
  geom_boxplot()+
  geom_signif(test="t.test",comparisons = list(c("Low Risk","High Risk")),annotation = "*")+
  theme_classic()+
  scale_fill_manual(values=c("#fc8d62","#66c2a5"))

billit.1 <- billit+
  labs(x="Risk Establshed by Weight to Height Ratio",
       y= "Pelvic Bredth (cm)",
       fill="Gender")+
  theme(legend.position="bottom")

billit.1
billit.1
#ggsave("billi1.1.png", plot = billi1.1, width = 8, height = 6, dpi = 300)

t.test(data=bdy,Biiliac~whtrrisk)
```


```{r next steps}
# whats next?
###linear model
fit.lm <- lm(whtr ~ Biiliac, data = bdy)
plot(fit.lm)
bdy05 <- bdy %>%
  mutate(
    pred_whtr = predict(fit.lm),             
    error = whtr - pred_whtr,                
    misclassified = ifelse(abs(error) > 0.05, "Yes", "No") 
  )
bdy01 <- bdy %>%
  mutate(
    pred_whtr = predict(fit.lm),             
    error = whtr - pred_whtr,                
    misclassified = ifelse(abs(error) > 0.01, "Yes", "No") 
  )
bdy03 <- bdy %>%
  mutate(
    pred_whtr = predict(fit.lm),             
    error = whtr - pred_whtr,                
    misclassified = ifelse(abs(error) > 0.03, "Yes", "No") 
  )

error_plot5 <- ggplot(bdy05, aes(misclassified, fill = Gender)) +
  geom_bar(position = "dodge") +
  theme_classic() +
  scale_fill_manual(values = c("#fc8d62","#66c2a5")) +
  labs(y = "Count", x = "Prediction Error > 0.05")

error_plot5
###Scrap these
error_plot1 <- ggplot(bdy01, aes(misclassified, fill = Gender)) +
  geom_bar(position = "dodge") +
  theme_classic() +
  scale_fill_manual(values = c("#fc8d62","#66c2a5")) +
  labs(y = "Count", x = "Prediction Error > 0.01")
error_plot3 <- ggplot(bdy03, aes(misclassified, fill = Gender)) +
  geom_bar(position = "dodge") +
  theme_classic() +theme(legend.position = "none")+
  scale_fill_manual(values = c("#fc8d62","#66c2a5")) +
  labs(y = "Count", x = "Prediction Error > 0.03")

combined_plot <- error_plot5+error_plot3+error_plot1
  plot_layout(guides = "collect") & 
  theme(legend.position = "bottom")

combined_plot

#ggsave("ldamist.png", plot = ldamistakes, width = 8, height = 6, dpi = 300)

summary(fit.lm)$adj.r.squared 

#####LDA#####

fit.18 <- lda(whtrrisk~Biiliac,data=bdy)
pred1 <- predict(fit.18)
pred.class <- pred1$class
pred.class
table(pred1$class,bdy$whtrrisk)
bdy2 <- bdy
bdy2$lda_class <- pred1$class
bdy2$LD1 <- pred1$x[,1] 
bdy2$pred_class <- pred1$class

bdy2 <- bdy2 %>%
  mutate(misclassified = ifelse(whtrrisk != pred_class, "Yes", "No"))

ldamistakes <- ggplot(bdy2, aes(misclassified,fill=Gender))+
  geom_bar(position="dodge")+theme_classic()+
  scale_fill_manual(values=c("#fc8d62","#66c2a5"))+
  labs(y="Count",x="Missclassified")+facet_wrap(vars(age_grouping))
  
#ggsave("ldamist.png", plot = ldamistakes, width = 8, height = 6, dpi = 300)

#get the formula
coef <- fit.18$scaling

coef
cat("LD1 =",coef,"* Pelvic Bredth in cm")

##find percent accurate

actual_class <- factor(bdy$whtrrisk, levels = levels(pred.class))
actual_class 
cm <- table(Predicted = pred.class, Actual = actual_class)
cm

accuracy <- sum(diag(cm)) / sum(cm) * 100
accuracy


```


```{r Graveyard}
##Scrapped plot
ggplot(bdy2, aes(x = LD1, fill = whtrrisk)) +
  geom_density(alpha = 0.3, color = NA) +   # actual group density
  geom_rug(aes(color = misclassified),
           sides = "b", size = 1, alpha = 0.8) +
  scale_fill_viridis_d(option = "plasma", name = "Actual Group") +
  scale_color_manual(values = c("No" = "darkgrey", "Yes" = "red"), name = "Misclassified") +
  theme_classic() +
  labs(x = "Linear Discriminant 1 (LD1)",
       y = "Density") +
  theme(
    plot.title = element_text(hjust = 0.5),
    legend.position = "right"
  )


```
```{r find those packages}

#search for packages.
library(stringr)

search_package_usage <- function(file, pkg, ignore_comments = TRUE) {
  # Read Rmd
  rmd_lines <- readLines(file)
  
  # Identify code chunks
  start <- grep("^```\\{r", rmd_lines)
  end   <- grep("^```$", rmd_lines)
  if(length(start) == 0) stop("No R code chunks found")
  
  code_lines <- character()
  code_line_numbers <- integer()
  
  for(i in seq_along(start)) {
    s <- start[i]
    e <- end[end > s][1]
    chunk <- rmd_lines[(s+1):(e-1)]
    
    if(ignore_comments) {
      non_comment_idx <- which(!grepl("^\\s*#", chunk))
      chunk <- chunk[non_comment_idx]
      lines_nums <- (s+1):(e-1)
      lines_nums <- lines_nums[non_comment_idx]
    } else {
      lines_nums <- (s+1):(e-1)
    }
    
    code_lines <- c(code_lines, chunk)
    code_line_numbers <- c(code_line_numbers, lines_nums)
  }
  
  # Package functions
  if(!requireNamespace(pkg, quietly = TRUE)) stop(paste0("Package ", pkg, " not installed"))
  pkg_funs <- ls(paste0("package:", pkg))
  pattern <- paste0("\\b(", pkg, "::)?(", paste(pkg_funs, collapse="|"), ")\\b")
  
  # Search each line and expand multiple matches
  results <- data.frame(line_in_rmd = integer(),
                        matched_text = character(),
                        full_line = character(),
                        stringsAsFactors = FALSE)
  
  for(i in seq_along(code_lines)) {
    matches <- str_extract_all(code_lines[i], pattern)[[1]]
    if(length(matches) > 0) {
      results <- rbind(
        results,
        data.frame(
          line_in_rmd = rep(code_line_numbers[i], length(matches)),
          matched_text = matches,
          full_line = rep(code_lines[i], length(matches)),
          stringsAsFactors = FALSE
        )
      )
    }
  }
  
  results
}

#do not put "ape" in, it will crash
pkgs <- c(
  "OTE", "tidyr", "psych", "ggplot2", "dplyr", "kableExtra", "pheatmap",
  "dendextend", "mice", "naniar", "forcats", "GGally", "gt", "viridis",
  "RColorBrewer", "plotly", "reshape2", "gridExtra", "descr", "plyr",
  "ggthemes", "stringr", "FactoMineR", "MASS", "ggdendro", "corrplot",
  "gtsummary", "ggsignif", "ggpubr", "tibble", "webshot2", "patchwork"
)

all_usage <- data.frame(package = character(),
                        matched_text = character(),
                        stringsAsFactors = FALSE)

# Loop through packages
for(pkg in pkgs) {
  usage <- search_package_usage("ANP 846 Manuscript.Rmd", pkg)
  
  if(nrow(usage) > 0) {
    usage$package <- pkg
    usage <- usage[, c("package", "matched_text")]
    all_usage <- bind_rows(all_usage, usage)
  }
}
if(nrow(all_usage) == 0) {
  stop("No package functions found in the Rmd file.")
}

unique_usage <- all_usage %>%
  distinct(package, matched_text)
unique_usage

package_summary <- aggregate(
  matched_text ~ package,
  data = unique_usage,
  FUN = function(x) paste(x, collapse = ", ")
)
package_summary <- package_summary[order(package_summary$package), ]

package_summary



unique_usage <- all_usage %>%
  distinct(package, matched_text)


summary_table <- package_summary %>%
  gt() %>%
  tab_header(
    title = "Functions Used per Package",
    subtitle = "Extracted from R Markdown"
  ) %>%
  cols_label(
    package = "Package",
    matched_text = "Functions"
  ) %>%
  tab_options(
    table.width = pct(100),
    heading.title.font.size = 16,
    heading.subtitle.font.size = 12,
    data_row.padding = px(3)
  )%>%
  tab_style(
    style = cell_text(align = "center"), 
    locations = cells_column_labels(everything())
  )


summary_table
#gtsave(summary_table, "package_functions_summary.png")
```



```{r table generation for paper bmi}



  
  
####  
tab3.0 <- bdy%>%
  dplyr::select(age_grouping,bmirisk,Gender)%>%
  mutate(Age = paste(age_grouping))%>%
   mutate(whtrrisk = paste(bmirisk,"Body Mass Index")) %>%
  tbl_strata(strata=Gender,
             .tbl_fun = ~.x %>%
               tbl_summary(by=bmirisk,include = age_grouping,label = list(age_grouping ~ "Age Group"))%>%
               add_n(),
             .header = "**{strata}**",N={n}
            )
tab3.0
gt3.0 <- as_gt(tab3.0)
gt3.0
#gtsave(gt3.0,"BMIRISK.png")



```

```{r graph creation bmi}

billi1.0 <- ggplot(bdy,aes(bmirisk,Biiliac,fill=Gender))+
  geom_boxplot()+
  geom_signif(comparisons = list(c("Low Risk","High Risk")),annotation = "*")+
  theme_classic()+
  scale_fill_manual(values=c("#fc8d62","#66c2a5"))

billi1.10 <- billi1.0+
  labs(x="Risk Establshed by Body Mass Index",
       y= "Pelvic Bredth (cm)",
       fill="Gender")+
  theme(legend.position="bottom")

billi1.10
#ggsave("billi1.10.png", plot = billi1.10, width = 8, height = 6, dpi = 300)

t.test(data=bdy,Biiliac~bmirisk)
```


```{r next steps BMI}
# whats next?
###linear model
fit.lm.0 <- lm(bmi ~ Biiliac, data = bdy)
plot(fit.lm.0)
bdy05.0 <- bdy %>%
  mutate(
    pred_bmi = predict(fit.lm.0),             
    error = bmi - pred_bmi,                
    misclassified = ifelse(abs(error) > 0.05, "Yes", "No") 
  )
bdy01.010 <- bdy %>%
  mutate(
    pred_bmi = predict(fit.lm.0),             
    error = bmi - pred_bmi,                
    misclassified = ifelse(abs(error) > 0.1, "Yes", "No") 
  )
bdy03.0 <- bdy %>%
  mutate(
    pred_bmi = predict(fit.lm.0),             
    error = bmi - pred_bmi,                
    misclassified = ifelse(abs(error) > 0.03, "Yes", "No") 
  )

error_plot5.0 <- ggplot(bdy05.0, aes(misclassified, fill = Gender)) +
  geom_bar(position = "dodge") +
  theme_classic() +
  scale_fill_manual(values = c("#fc8d62","#66c2a5")) +
  labs(y = "Count", x = "Prediction Error > 0.05")

error_plot5.0

error_plot1.010 <- ggplot(bdy01.010, aes(misclassified, fill = Gender)) +
  geom_bar(position = "dodge") +
  theme_classic() +
  scale_fill_manual(values = c("#fc8d62","#66c2a5")) +
  labs(y = "Count", x = "Prediction Error > 0.1")
error_plot3.0 <- ggplot(bdy03.0, aes(misclassified, fill = Gender)) +
  geom_bar(position = "dodge") +
  theme_classic() +theme(legend.position = "none")+
  scale_fill_manual(values = c("#fc8d62","#66c2a5")) +
  labs(y = "Count", x = "Prediction Error > 0.03")

combined_plot.0 <- error_plot5.0+error_plot3.0+error_plot1.010+
  plot_layout(guides = "collect") & 
  theme(legend.position = "bottom")

combined_plot.0

#ggsave("ldamist.png", plot = ldamistakes, width = 8, height = 6, dpi = 300)

summary(fit.lm.0)$adj.r.squared 

#####LDA#####
fit.18.0 <- lda(bmirisk~Biiliac,data=bdy)
pred1.0 <- predict(fit.18.0)
pred.class1 <- pred1.0$class

table(pred1.0$class,bdy$whtrrisk)
bdy2.0 <- bdy
bdy2.0$lda_class <- pred1.0$class
bdy2.0$LD1 <- pred1.0$x[,1] 
bdy2.0$pred_class <- pred1.0$class

bdy2.0 <- bdy2.0 %>%
  mutate(misclassified = ifelse(bmirisk != pred_class, "Yes", "No"))

ldamistakes.0 <- ggplot(bdy2.0, aes(misclassified,fill=Gender))+
  geom_bar(position="dodge")+theme_classic()+
  scale_fill_manual(values=c("#fc8d62","#66c2a5"))+
  labs(y="Count",x="Missclassified")+facet_wrap(vars(age_grouping))

ldamistakes.0 
#ggsave("ldamist.0.png", plot = ldamistakes.0, width = 8, height = 6, dpi = 300)

#get the formula
coef.0 <- fit.18.0$scaling

coef.0
cat("LD1 =",coef.0,"* Pelvic Bredth in cm")

##find percent accurate
actual_class.0 <- factor(bdy$whtrrisk, levels = levels(pred.class1))
actual_class.0 
cm.0 <- table(Predicted = pred.class1, Actual = actual_class.0)
cm.0

accuracy.0 <- sum(diag(cm.0)) / sum(cm.0) * 100
accuracy.0

```